---
title: "HW1"
author: "Trevor Rizzi"
date: "2022-10-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework 1
### Question 1
Supervised learning: In supervised learning, the Y data is actually known and used for training the model.
                        Model is given the observed output and input (from lecture slides day 1)
Unsupervised learning: The response data is unknown, so the model is only given predictors and is to come up with a fit based on them

Supervised learning trains itself based on inputs and outputs while unsupervised has to determine the structure between inputs on its own.

### Question 2
In a regression model, Y is quantitative (numerical values) whereas classification is qualitative (categorical values) - (lecture slides day 1).
In machine learning a quantitative model will be numerically based and a classification model will have categorical labels instead.

### Question 3
Regression commonly used metrics: age, height
Classification commonly used metrics: color, win/ loss

### Question 4
Descriptive models: "Choose a model to best visually emphasize a trend in data" (lecture slides day 1)
Inferential models: "Aim is to test theories ... State relationship between outcomes and predictors" (lecture slides day 1)
Predictive models:  "Aim is to predict Y with minimum reducible error ... Not focused on hypothesis tests" (lecture slides day 1)

### Question 5
Mechanistic: Parametric, uses the parametric form to predict what could be observed.
Emperically-driven: Non-parametric, uses real observations to develop a theory.

Mechanistic models are typically less flexible but can that can differ based on # of parameters. Emperically driven models require a larger
quantity of observations

I think empirically-driven models are easier to understand since it is coming to a theoretical conclusion based off of real world events/obersvations. It is more straight forward.

It is ideal to simultaneously achieve a low variance and low bias. A simple model which is typically mechanistic will have a high bias and low variance. An empirical model will have a high flexibility and therefore a low bias and high variance

### Question 6
Given a voter’s profile/data, how likely is it that they will vote in favor of the candidate?
  This is predictive as the aim is to predict a Y (whether they will vote for a candidate) with minimum error.
How would a voter’s likelihood of support for the candidate change if they had personal contact with the candidate?
  This is inferential as it is trying to establish a relationship between the outcome (likelihood of support) and predictors(contact with candidate)


```{r}
install.packages("tidyverse",repos = "http://cran.us.r-project.org")
install.packages("tidymodels", repos = "http://cran.us.r-project.org")
install.packages("ISLR", repos = "http://cran.us.r-project.org")

library(tidyverse)
library(tidymodels)
library(ISLR)
```

###Exercise 1
```{r}
hwyMpg <- mpg$hwy
hist(hwyMpg)

```
The histogram is bimodal, with peaks its between 15-20 mpg and 25-30 mph suggesting that these ranges are the most common highway mileages.

### Exercise 2
```{r}
ggplot(mpg, aes(x = hwy, y = cty)) + geom_point()


```

The scatterplot suggests a linear relationship between cty and hwy. This means that as the city mileage increases, the highway mileage will also increase.

### Exercise 3
```{r}
ggplot(mpg, aes(y = reorder(manufacturer, manufacturer, function(x)-length(x)))) + geom_bar()

```
Dodge produced the most cars, lincoln produced the least.

### Exercise 4
```{r}
ggplot(mpg, aes(y = hwy, x = cyl, group = cyl)) + geom_boxplot()


```
As number of cylinders increases, the highway mileage tends to decrease

### Exercise 5
```{r}
install.packages("corrplot")
library(corrplot)

M <- mpg %>%
    select_if(is.numeric) %>%
    cor(.)

corrplot(M)

```

Number of cylinders and engine displacement are positively correlated, which makes sense because typically more cylinders = bigger engine
hwy and cty mileages are also positively correlated. Both the hwy and cty have a negative correlation with the number of cylinders, implying that engines with more cylinders are less efficient. 