---
title: "HW2"
author: "Trevor Rizzi"
date: "2022-10-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework 1

```{r}

library(ggplot2)
library(tidyverse)
library(tidymodels)
library(corrplot)
library(ggthemes)
library(dplyr)
tidymodels_prefer()
abalone <- data.frame(read_csv("/Users/trevorrizz/Downloads/homework-2/data/abalone.csv"));

```

### Question 1

```{r}

abalone <- abalone %>%
  mutate(age=rings + 1.5)


abalone %>% 
  ggplot(aes(x = age)) +
  geom_histogram(bins = 60) +
  theme_bw()


```
Abalone age resembles a normal distribution with a mean around 10 years of age.

### Question 2
```{r}
set.seed(12323)

abalone_split <- initial_split(abalone, prop = .85, strata = age)
abalone_train <- training(abalone_split)
abalone_test <- testing(abalone_split)



```


### Question 3
```{r}
abalone_recipe <- recipe(age ~ type + longest_shell + diameter + height + 
                        whole_weight + shucked_weight + viscera_weight + 
                        shell_weight, data = abalone_train) %>%
  step_dummy_multi_choice(all_nominal_predictors()) %>%
  prep()

summary(abalone_recipe)



abalone_recipe <- abalone_recipe %>%
  step_interact(~ type_F:type_I:type_M:shucked_weight + longest_shell:diameter + shucked_weight:shell_weight) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors())





```
We cannot use rings as a predictor for age because of how they were used to calculate the
age for each abalone. The number of rings and abalone age are linearly related, so using that
as a predictor would affect the model.


### Question 4
```{r}

lm_model <- linear_reg() %>% 
  set_engine("lm")


```


### Question 5
```{r}

lm_wflow <- workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(abalone_recipe)


```

### Question 6
```{r}
lm_fit <- fit(lm_wflow,abalone_train)

predict(lm_fit, new_data = expand.grid(longest_shell = .50,
                                       diameter = .10,
                                       height = .30,
                                       whole_weight = 4,
                                       shucked_weight = 1,
                                       viscera_weight = 2,
                                       shell_weight = 1,
                                       type = "F")) ### 24.03469 years


```

### Question 7
```{r}

library(yardstick)

abs_set <- metric_set(rsq, rmse, mae)

abs_tbl <- bind_cols(abalone_train$age, predict(lm_fit, abalone_train))

names(abs_tbl)[1] <- "truth"
names(abs_tbl)[2] <- "pred"


abs_set(abs_tbl, truth = truth , estimate = pred)

```


